### 2018-02-16 Physics Notes/Nuclear Physics/Nuclear Energy/Nuclear Energy.tex
Physics Notes Update

If the binding energies per nucleon of two different nuclides are compared, the nucleus with more binding energy per nucleon is the more stable of the two.

>>>>

If the binding energies per nucleon of two different nuclides are compared, the nucleus with more binding energy per nucleon is the more stable of the two.\\
\includegraphics[width=8cm]{Binding_Energy.jpg}\\
In \textbf{nuclear fission} the binding energy per nucleon increases as a large unstable nucleus splits into two more stable fragments.\\
In \textbf{nuclear fusion} the binding energy per nucleon increases, provided the nucleon number does not exceed the peak on the graph (around 50). This is why fusion can only occur on the left side of the graph as fusing iron would lose energy.\\
Atoms always want to increase binding energy, fusion goes right, fission goes left.
